Look, we can do something

### 2024-10-22 paper.tex
Rework definition of awesomeness (2/N)

Substituting \cref{eq:pre-awesomeness} and \cref{eq:intro} we get a new pore
shape parameter we call ``\highlight{awesomeness}'':
\begin{equation}
  \begin{aligned}
    P &= \frac{\pi [3(1+E) - \sqrt{(3E+1)(E+3)}]}{4E} \times \\
    & \times \inf \{\frac{\rho_{AB}}{L_{AB}} \ \forall (A, B) \in B^2\}
  \end{aligned}
  \label{eq:awesomeness}
\end{equation}
where, again, $E$ is the elongation and $B$ is the boundary of the pore.

\section{Computational algorithm}
\label{seq:alg}
Our algorithm for calculating \highlight{awesomeness} is quite simple. It
assumes that an image of a pore is made with sufficient resolution, so we can
use boundary pixels without any additional processing. The main algorithm
consists of three parts and is shown in \cref{alg:main}.
\begin{algorithm}[H]
  \caption{Algorithm for computation of \highlight{awesomeness} of a pore.}
  \label{alg:main}
  \begin{algorithmic}[1]
    \Procedure{\texttt{awesomeness}}{\texttt{img}}
    \State \texttt{bs $\gets$ boundary(img)}
    \Comment Construct a list of boundary points (\cref{alg:extraction}).
    \State \texttt{\%bs $\gets$ sort(bs)}
    \Comment Sort points as described in \cref{alg:sort}.
    \State \textbf{return} \texttt{pmin(\%bs)}
    \Comment The final step is in \cref{alg:pmin}.
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

@@

Summarly 3901 images out of 4000 (97.5\%) were good enough for \texttt{sort} to
sort boundary points in pores. For these images we also computed commonly used
convexity and elongation parameters. On \cref{fig:cae-space} each pore is
represented as a dot in convexity-elongation-\highlight{awesomeness} (CEA)
space.
\begin{figure*}
  \centering
  \subfigure[Convexity-elongation-\highlight{awesomeness} space]{
    \includegraphics[width=0.4\linewidth]{images/cae.png}
    \label{fig:cae-space}}
  \hfill
  \subfigure[Convexity-elongation-roundness space]{
    \includegraphics[width=0.4\linewidth]{images/cer.png}
    \label{fig:cer-space}}
  \vskip\baselineskip
  \subfigure[Elongation-\highlight{Awesomeness} space]{
    \includegraphics[width=0.4\linewidth]{images/ae.png}
    \label{fig:ae-space}}
  \hfill
  \subfigure[Convexity-elongation-\highlight{improved awesomeness} space]{
    \includegraphics[width=0.4\linewidth]{images/caei.png}
    \label{fig:caei-space}}
  \caption[]{Synthetically generated pores shown as points in different
    parameter spaces.}
  \label{fig:parameter-spaces}
\end{figure*}

@@

% CHECK THIS:
Indeed, on \cref{fig:caei-space} we see that improved awesomeness is less
correlated with elongation.

Another common parameter for describing pore shapes is roundness. Figure
\ref{fig:cer-space} features convexity-elongation-roundness (CER) space.
It can be seen that roundness-convexity correlation is bigger than
awesomeness-convexity correlation. All correlation values are in
\cref{tab:correlations}.
\begin{table*}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Awesomeness & Elongation & Convexity & Roundness \\
    \hline
    Awesomeness & 1 & 0.049 & 0.557 & 0.745 \\
    \hline
    Elongation & & 1 & 0.457 & 0.355 \\
    \hline
    Convexity &&& 1 & 0.922 \\
    \hline
    Roundness &&&& 1 \\
    \hline
  \end{tabular}
  \caption{Correlation between shape describing parameters.}
  \label{tab:correlations}
\end{table*}

>>>>

Substituting \cref{eq:pre-awesomeness} and \cref{eq:intro} we get a new pore
shape parameter we call ``\highlight{awesomeness}'':
\begin{equation}
  \begin{aligned}
    P &= \frac{\pi [3(1+E) - \sqrt{(3E+1)(E+3)}]}{4E} \times \\
    & \times \inf \{\frac{\rho_{AB}}{L_{AB}} \ \forall (A, B) \in B^2\}
  \end{aligned}
  \label{eq:awesomeness}
\end{equation}
where, again, $E$ and $B$ are the elongation the boundary of the pore,
$\rho_{AB}$ is the Euclidean distance between points $A$ and $B$ and $L_{AB}$ is
the length of a path (the shortest one) between $A$ and $B$ along the boundary.

\section{Computational algorithm}
\label{seq:alg}
Our algorithm for calculating \highlight{awesomeness} is quite simple. It
assumes that an image of a pore is made with sufficient resolution, so we can
use boundary pixels without any additional processing. The main algorithm
consists of three parts and is shown in \cref{alg:main}.
\begin{algorithm}[H]
  \caption{Algorithm for computation of \highlight{awesomeness} of a pore.}
  \label{alg:main}
  \begin{algorithmic}[1]
    \Procedure{\texttt{awesomeness}}{\texttt{img}}
    \State \texttt{bs $\gets$ boundary(img)}
    \Comment Construct a list of boundary points (\cref{alg:extraction}).
    \State \texttt{\%bs $\gets$ sort(bs)}
    \Comment Sort points as described in \cref{alg:sort}.
    \State \textbf{return} \texttt{c $\cdot$ pmin(\%bs)}
    \Comment The final step is in \cref{alg:pmin}. \texttt{c} is the fraction in
    \cref{eq:awesomeness}.
    \EndProcedure
  \end{algorithmic}
\end{algorithm}

@@

Summarly 3901 images out of 4000 (97.5\%) were good enough for \texttt{sort} to
sort boundary points in pores. For these images we also computed commonly used
convexity and elongation parameters. On \cref{fig:cae-space} each pore is
represented as a dot in convexity-elongation-\highlight{awesomeness} (CEA)
space.
\begin{figure*}
  \centering
  \subfigure[Convexity-elongation-\highlight{awesomeness} space]{
    \includegraphics[width=0.4\linewidth]{images/cae.png}
    \label{fig:cae-space}}
  \hfill
  \subfigure[Convexity-elongation-roundness space]{
    \includegraphics[width=0.4\linewidth]{images/cer.png}
    \label{fig:cer-space}}
  \vskip\baselineskip
  \subfigure[Elongation-\highlight{Correlated awesomeness} space]{
    \includegraphics[width=0.4\linewidth]{images/ae.png}
    \label{fig:ae-space}}
  \caption[]{Synthetically generated pores shown as points in different
    parameter spaces.}
  \label{fig:parameter-spaces}
\end{figure*}

@@

Another common parameter for describing pore shapes is roundness. Figure
\ref{fig:cer-space} features convexity-elongation-roundness (CER) space.
It can be seen that roundness-convexity correlation is bigger than
awesomeness-convexity correlation. All correlation values are in
\cref{tab:correlations}.

On \cref{fig:ae-space} pores are shown in $p-E$ space where $p$ is a
``correlated'' \highlight{awesomeness} parameter \cref{eq:pre-awesomeness}. It
shows that our assumption on the maximal value of \highlight{awesomeness} is
correct indeed.

\begin{table*}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    & Awesomeness & Elongation & Convexity & Roundness \\
    \hline
    Awesomeness & 1 & 0.049 & 0.557 & 0.745 \\
    \hline
    Elongation & & 1 & 0.457 & 0.355 \\
    \hline
    Convexity &&& 1 & 0.922 \\
    \hline
    Roundness &&&& 1 \\
    \hline
  \end{tabular}
  \caption{Correlation between shape describing parameters.}
  \label{tab:correlations}
\end{table*}
